Lifting CDCL to Relational Domains

### 2016-10-15 domains.tex
various fixes

%-------------------------------------------------------------------------------
\paragraph{Abstract Transformers}
%
%In a typical abstract interpretation based Galois-connection setting
%over an over-approximate domain, every concrete element has a unique
%over-approximate representation in the abstract.  Likewise, every
%concrete transformer is over-approximated by a unique abstract
%transformer.  We now define an abstract deduction transformer.
%
An abstract transformer transforms an abstract value $a$ through a
statement $s$, i.e.\ it \emph{deduces} information from $a$ and $s$.
The best abstract transformer is
\[\llbracket s
\rrbracket^\sharp(a)=\min \{a'\mid a'\models s\}\] 
where we write
$a\models s$ if $\forall \vec{y}\in\gamma(a): (s[\vec{y}/\vec{x}]
\equiv \true)$, i.e.\ the constraint $s$ is valid when evaluated over
all values $\vec{y}$ of its variables $\vec{x}$ in the concretisation
of $a$. Any abstract transformer that computes a non-minimal element
is still a sound over-approximating transformer and can be used in our
algorithm.

@@

Standard abstract interpretation does not require complementation property.  
Abstract Domain library, such as APRON C library~\cite{apron} is specialized 
for abstract interpretation.  We implement a template-based polyhedra domain 
that returns precise complements by decomposing it into half-spaces.

>>>>

%-------------------------------------------------------------------------------
\paragraph{Abstract Transformers}
%
%In a typical abstract interpretation based Galois-connection setting
%over an over-approximate domain, every concrete element has a unique
%over-approximate representation in the abstract.  Likewise, every
%concrete transformer is over-approximated by a unique abstract
%transformer.  We now define an abstract deduction transformer.
%
An abstract transformer transforms an abstract value $a$ through a
statement $s$, i.e.\ it \emph{deduces} information from $a$ and $s$.
The best abstract transformer is
\[\llbracket s
\rrbracket^\sharp(a)=\bigsqcup \{a'\mid a'\models s\}\] where we write
$a\models s$ if $\forall \vec{y}\in\gamma(a): (s[\vec{y}/\vec{x}]
\equiv \true)$, i.e.\ the constraint $s$ is valid when evaluated over
all values $\vec{y}$ of its variables $\vec{x}$ in the concretisation
of $a$. Any abstract transformer that over-approximates the least
upper bound is a sound transformer and can be used in our algorithm.

@@

Standard abstract interpretation does not require a complementation
operator. Hence, abstract domain libraries, such as APRON~\cite{apron}
do not provide it.  However, it can be implemented with the help of a
meet decomposition as explained above.
%
Another feature that abstract domain libraries do not provide is to
track the reasons why certain deductions have been made. We come back
to this point in Section~\ref{sec:abst}.

### 2016-10-15 experiments.tex
refactoring domain.tex figure 2
various fixes

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains 
in 2LS verification tool~\cite{2ls}.  The abstract domains used for 
our experiments are intervals, template polyhedra, octagons and equalities.  
We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC and a 
commercial static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT 
solver in the backend.  Astr{\'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  All the 
bounded loops are completely unrolled in Astr{\'e}e.

>>>>

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains
in 2LS verification tool~\cite{2ls}.  We used the abstract domains
provided by 2LS (intervals, octagons and equalities) for our
experiments. Although the performance of these implementations is not
competitive with dedicated implementations as found in
APRON~\cite{apron}, for instance, they have the advantage that they
handle all C operators (including bitwise operations) out of the box.

We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC and a 
commercial static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT 
solver in the backend.  Astr{\'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  All the 
bounded loops are completely unrolled in Astr{\'e}e.
